\emph{Cree}: A modern toolbox for readymade economic experiments

### 2015-06-22 Latex/paper.tex
Appendix: Source code and fieldnotes

\section{List of \Cree dependencies}

@@

>>>>

\section{\Cree dependencies}

@@

\section{Source code}

The source code for \Cree is licensed under the MIT license and available at \url{https://github.com/jsekamane/Cree}. An example experiment of an English auction is available at \url{https://github.com/jsekamane/Cree/tree/master/examples/english-auction}. Fieldnotes for this paper is available at \url{https://github.com/jsekamane/Cree-Paper}.
